---
title: "Data Visualization with ggplot2"
author: "Maria Tackett"
date: "05.12.20"
output:
  xaringan::moon_reader:
  #  mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    css: "slide-design.css"
 #   logo: img/sta210-sticker-icon.png
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: 16:9
---

### Goals for today 

- list of goals on left 
- output of what they can make on right

---

### `ggplot2`

- part of tidyverse
- grammar of graphics
- plots built in layers

```{r}
library(tidyverse)
```

---

### example plot and code

- Use diamonds dataset

---

### Basic `ggplot` syntax

```{r eval = F}
ggplot(data = [dataset], aes(x = [x-var], y = [y-var])) +
  geom_xx() + 
  other options
```


---

### diamonds data

```{r diamond-plot, include = F}
ggplot(data = diamonds, aes(x = carat, y = price)) +
  geom_point() + 
  labs(title = "title", 
       x = "carat",
       y = "price")
```

---

### Live demo, let's see what's happening. 


---

### Adding aesthetics

What's the different between two plots ?

color all points
color by variable 

---

### Aesthetics 

 Show types, 
 
 size, alpha, etc. 
 
--- 
 
### Formative assessment
Multiple choice question 

---

### Put it all together 

- Live demo 

---

### Last assessment




 

