---
title: "Data Visualization"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r echo = F}
library(learnr)
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
```

```{r setup, echo = F}
library(ggplot2)
library(dplyr)
library(forcats)
library(lubridate)
library(mosaicData)

Riders <- Riders %>%
  mutate(month = month(date)) %>%
  mutate(month = case_when(
    month == 4 ~ "April", 
    month == 5 ~ "May", 
    month == 6 ~ "June", 
    month == 7 ~ "July", 
    month == 8 ~ "August", 
    TRUE ~ "November"
  ), 
  day = fct_relevel(day, "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
```

## Exercise 1: Aesthetics

Consider the code below: 

```{r echo = TRUE, eval = FALSE}
ggplot(data = diamonds, aes(x = carat, y = price)) +
  geom_point(aes(shape = cut), color = "blue")
```

```{r aes-quest}
question("Which of the following best describes the points on the plot?",
    answer("The shape is the same for all points."),
    answer("The color is the same for all points.", correct = TRUE),
    answer("The color and shape are the same for all points.")
  )
```

## Exercise 2: Putting it all together

Let's put everything we've learned to visualize the relationship between multiple variables. For the following exercises, we will use the `Riders` dataset from the mosaicData R package. This dataset contains daily information on the weather conditions and number of users on a Massachusetts rail trail. The data were collected from April 5, 2005 to November 15, 2005. You can learn more about the dataset by typing `??mosaicData::Riders` in the console. 

For now, we will focus on the following variables: 

- `highT`: high temperature for the day (in degrees Fahrenheit)
- `lowT`:  low temperature for the day (in degrees Fahrenheit)
- `clouds`: measure of cloud cover (in oktas)
- `precip`: inches of precipitation
- `weekday`: type of day (N: weekend or holiday, Y: non-holiday weekday)
- `day`: day of the week (Monday, Tuesday, Wednesday, etc.)
- `riders`: estimated number of trail users that day
- `month`: month extracted from `date`

### Part 1

Recreate the plot shown below by filling in the missing values in the code chunk.

```{r echo = FALSE, eval = TRUE}
ggplot(data = Riders, aes(x = highT, y = riders, color = clouds)) + 
  geom_point() + 
  labs(x = "High Temperature", 
       y = "Riders", 
       color = "Cloud Cover",
       title = "Riders vs. High Temp. & Cloud Cover", 
       subtitle = "Faceted by Weekday") +
  facet_wrap(~ weekday)
```


```{r parsons-1, exercise = TRUE}
# Replace the blanks with the correct values. 

ggplot(data = Riders, aes(x = highT, y = _____, color = _____)) + 
  geom_point() + 
  labs(x = "_____", 
       y = "Riders", 
       color = "Cloud Cover",
       title = "Riders vs. High Temp. & Cloud Cover", 
       subtitle = "_____") +
  facet_wrap(~ _____)

```

### Part 2

Recreate the plot shown below by filling in the missing values in the code chunk.

```{r echo = FALSE, eval = TRUE}
ggplot(data = Riders, aes(x = clouds, y = precip, color = weekday)) + 
  geom_point() + 
  labs(x = "Cloud Cover", 
       y = "Precipitation", 
       color = "Weekday",
       title = "Precipitation vs. Cloud Cover & Weekday", 
       subtitle = "Faceted by Month") +
  facet_wrap(~ month)
```

```{r parsons-2, exercise = TRUE}
# Replace the blanks with the correct values. 

ggplot(data = Riders, aes(_____)) + 
  geom_point() + 
  labs(_____)+
  facet_wrap(_____)
```

### Part 3

Recreate the plot shown below. 

```{r echo = FALSE, eval = TRUE}
ggplot(data = Riders, aes(x = lowT, y = riders, color = day)) + 
  geom_point() + 
  labs(x = "Low Temperature", 
       y = "Riders", 
       color = "Day",
       title = "Riders. vs. Low Temp & Day", 
       subtitle = "Faceted by Month") +
  facet_wrap(~ month)
```

```{r parsons-3, exercise = TRUE}
# Write code to recreate the plot.

```

